Kaggle-in-class Data Challenges can Boost Student Learning

### 2018-03-08 paper-kaggle.Rmd
added abstract, need to work out why title doesn't show

---
title: Kaggle-in-class Data Challenges can Boost Student Learning
# to produce blinded version set to 1
# blinded: 0
author: 
  - name: Julia Polak
    affiliation: Department of Statistics, University of Melbourne
  - name: Dianne Cook
    affiliation: Department of Econometrics and Business Statistics, Monash University
bibliography: bibliography.bib
link-citations: true
fig_caption: yes
#keywords:
#- 3 to 6 keywords
#- that do not appear in the title
abstract: >
  The text of your abstract.  200 or fewer words.
output: rticles::asa_article
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(knitcitations)
library(RefManageR)
library("tidyverse")
library("ggpubr")
library("readxl")
library("gridExtra")

>>>>

---
title: Kaggle-in-class Data Challenges can Boost Student Learning
# to produce blinded version set to 1
# blinded: 0
author: 
  - name: Julia Polak
    affiliation: Department of Statistics, University of Melbourne
  - name: Dianne Cook
    affiliation: Department of Econometrics and Business Statistics, Monash University
bibliography: bibliography.bib
link-citations: true
fig_caption: yes
keywords: technology, statistical modeling, data science, statistics education
#- that do not appear in the title
abstract: >
  Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants. Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting. This paper describes the results of an experiment to determine if the participating in a predictive modeling competition enhances learning. The evidence suggests it does. In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
output: rticles::asa_article
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(knitcitations)
library(RefManageR)
library("tidyverse")
#library("ggpubr")
library("readxl")
library("gridExtra")
